\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{siunitx} 
\usepackage{subcaption}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{enumitem}
\usepackage{cancel}
\usepackage{wrapfig}
\usepackage{imakeidx}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{hyperref} 
\usepackage[margin=1in]{geometry}

\usepackage{subfiles}



\title{Business Notes}
\author{Joshua Liu}
\date{\today}


\begin{document}
\maketitle

\section{Introduction}
Thanks Erica for some of the Notes

\section{Economy}
Economies have traditionally relied on people working. However, because of advancements in automation, AI, and technology in general. Workers are encountering a variety of challenges. It is now a precarious workforce. What does precarious mean?
\begin{itemize}
    \item Lots of uncertainty in the workforce, what create this uncertainty?
    \begin{itemize}
        \item Automation and robotics have limited or erased many jobs.
    \end{itemize}
    \item Lots of stress because so much is unknown, how will our financial situation be in the future?
    \begin{itemize}
        \item Can we retire with money in the bank?
        \item Can we pay for our kids education?
    \end{itemize}
    \item Temporary, More contract work (not permanent)
    \begin{itemize}
        \item Factory work (highly automated)
        \item Fast food
        \item Transportation (Uber)
    \end{itemize}
\end{itemize}

\begin{itemize}
    \item Precarious influence every industry whether private or public
    \item Evan advanced level jobs are to deal with precarious jobs
    \item Uncertaintity leads to financial instability
    \item Management has a vital role to play
\end{itemize}

Lets continue to understand what the economy looks like today

Lets identify some characteristics that help us understand our current economic state

\begin{enumerate}
    \item Virtual workplace $\rightarrow$ medical consultations, engineer consultants, educators, non-essential workers.
    \item Recessionary $\rightarrow$ economy shrinking, stock prices, high unemployment rate, she-cession (Recession that primarily impacts women)
    \item Precarious $\rightarrow$ The uncertainty that the gig economy produces (free lancing workers being replaced, or working less hours or more hours, because of technology), no job security, no holiday/no vacation, work on demand, no sickdays, less education required, no workplace benefits, no retirement savings
\end{enumerate}

Governments have a role to play. Governments they want to protect jobs and be seen as creating jobs but they also like to attract technology companies, so there is a contradiction - technology companies can easily remove jobs through automation but governments spend lots of money and other resources to attract these tech companies. But, tech companies will kill jobs but governments spends a lot of money to attract these companies

Ontario is trying very had to attract Amazon 

\begin{itemize}
    \item What is the impact of Amazon on local retailers
    \item What is the impact of Amazon on suppliers
    \item How can government manage a company like Amazon or is Amazon basically unstoppable
    \item How can we make sure Amazon workers feel recognized and valued
    \item Why would Ontario try so hard to attract Amazon list some reasons
\end{itemize}

\begin{itemize}
    \item One large impact Amazon will have on retailers would be the competition as Amazon is (the largest?) company have been known to use aggressive tactics to force other businesses out of the market. 
    \item I think the same applies to suppliers, Amazon has its finger in every pie. For suppliers, its Amazon Basics.     
    \item I also think governments would not or would have little influence over Amazon as Amazon is a large company and I think it's easier for Amazon to influence the government with its money through lobbying.    
    \item I don't know.
    \item I think Ontario is trying very hard to attract Amazon as bringing Amazon over would bring over businesses as well. 
\end{itemize}

\textbf{QUESITON:} Does society owe the worker anything?

Government's impact on workforce
\begin{itemize}
    \item Employee insurance, gives money to unemployed
    \item Corporate taxes, are too high or low
    \item Steer the economy into a certain direction, tech heavy (Amazon)
    \item Make and create laws, minimum wage, is it too high or low?
    \item They can create levels of uncertainty and certainties, 
    \item Anti-discrimination laws
    \item Should businesses provide onsite childcare?
    \item Should businesses only priority be making profits?
\end{itemize}

\subsection{Test}

Format: Case study, single page (double sided)

Study:
\begin{itemize}
    \item Precarious
    \item Gig economy
    \item Government influence in rules regarding workplace
    \item Role of women and BIPOC in the workforce
\end{itemize}

\section{Tangledness}
As managers we should familiarize ourselves with some important business concepts, one we will look at is globalization. The traditional definition of globalization is the inter-connectivity between countries, people, business, and governments. A more nuanced description of globalization is the tanglement of countries, people, business, and Government. What do we mean by being tangled? What impacts a person or business in another country will impact you or a person somewhere else.

Some concepts of a tangled world is 

\begin{itemize}
    \item Economies
    \item Political
    \item Social issues
    \item Foreign
    \item Climate change
\end{itemize}

Globalization impact on workers - globalization benefits and downsides - tangled

One of the great accelerant of globalization has been social media - social media has done some good but now it's mostly a wasteland - it has spurred some positive social movements - let's identify some of these positive movements
\begin{itemize}
    \item MeToo movements
    \item Black Lives Matter
    \item Climate Change Advocacy
    \item Environmental
    \item Bell Let's Talk Day
    \item Indigenous causes
\end{itemize}

From a management perspective, social media can represent something strong but the problem with social media is the speed at which a company's errors can be discussed and seen - Hootsuite.

Let's identify the problem - the company signed a contract with an organization that is seen harsh on deporting newcomers or oldcomers from the US (ICE)

As a manager of Hootsuite - how can we solve this problem

\begin{itemize}
    \item Internal voting system especially for highly polarized issues - treat your employees well and give them power and influence
    \item Re-connect with companies that does exhibit good social responsibility - World Wildlife Fund, activists
    \item Work on building unity in the company - majority of employees should agree with certain contracts
    \item Encourage employees to speak up but do so first within the business and then if no action is taken, feel free to publicize your views.
\end{itemize}

How can we use social media for good (instead of the misinformation and the disinformation)

\begin{itemize}
    \item Raise awareness
    \item Take opinons from the public - we have to do that carefully - be careful what you associate your business with and who you associate your business with
    \item Social media plan - how to handle problems or criticisms of your brand
    \item Pro-active - don't sit around waiting to prevent bad news
\end{itemize}

Describe a social media plan - speak and promote views that the company believes in and the products and services that the business sells

The 3 C's of business management

\begin{itemize}
    \item Certainty - How can a business achieve certainty (This is very difficult) - long term contracts, have good brand power (larger companies tend to do better than smaller companies with brand power), keep employee turnover down. Getting to know your customer as well as you can, be really flexible, roll with the punches, partner with someone who can help
    \item Consistency - Quality control, timeline for goals, retain employees, rules and regulations - restaurants are a great example of an industry that needs Consistency
    \item Clarity - transparency - the ability to see through - honesty - be open about your business - where you get resources, your sustainability records - build trust
\end{itemize}

Let's look at a company and write about why it is so difficult to achieve the 3 C's of management

Nestle, things this company relies on to succeed

\begin{itemize}
    \item Farmers
    \item Retail Stores
    \item Suppliers
    \item Shipping Vessels
    \item Trucking and Rail
    \item Oil and Gas industry - often make plastics - packaging
    \item Management to make good decisions
\end{itemize}


Does Nestle achieve the 3 C's? No, because this company operates in such a volatile planet - border closures, pandemic, poorer economic conditions, climate change, political changes.

Is Doug Ford doing a good job managing the pandemic?

\begin{enumerate}
    \item Characteristics of a manager - strong personality, leadership, confidence, problem solving, charismatic, planner, focus, organized, willing to take chance, informed and knowledgeable
\end{enumerate}

\begin{itemize}
    \item Made a decisive decision during the pandemic and stuck to it
    \item Make the decision to keep his decision and enforce certain rules
    \item Provides open reports and keep people informed
    \item A large amount uncertainty in school reopening
    \item Focused on reopening and lowering the curve.
    \item Calls out people who aren't follow the rules.
\end{itemize}

Important workforce trends

\begin{itemize}
    \item Diversity - diversity in thought and decision making - perspectives, wisdom, lived experience
    \item Aging workforce - more older people than younger people in this country - people over the age of 65 years old than people younger than 15 years old
    \item The emphasis on climate change - the impacts of that on the workforce
\end{itemize}

Let's identify countries like Canada that have older populations - Japan, USA, Italy, Russia

Let's identify countries that have younger populations - China, India, Croatia, African countries, Iran

In general, people need to replace the older population with at least two children. Our replacement rate in Canada is close to 1.4

Benefits of having an older workforce 

\begin{itemize}
    \item More experience - More knowledge
    \item Stronger work ethic - versus young people who work in different ways
    \item Different skill set
    \item Management can relate to older workers better if management themselves is older
    \item Risk averse - cost the company less money 
\end{itemize}

Cons of having an older workforce

\begin{itemize}
    \item Harder for young workers to advance as older workers retain their positions
    \item Technology barrier for some older people - company has to spend money and resources to possibly train older employees
    \item Strain on health care system
    \item Older ideas
\end{itemize}

From a society standpoint here is the big problem of an older workforce: decreasing tax base - less workers because of retirement or old age. Then the government will collect less tax and therefore will have less money to spend on public resources such as healthcare and education

What are some solutions to this problem of an aging workforce: 

\begin{itemize}
    \item Incentives to have kids - Maternity leave, paternity leave, baby bonus
    \item *Child care - affordable, should it be universal?
    \item *Immigration policy 
    \item *Keep the older workforce working, extend the retirement age to an older age
    \item Government incentives - help parents with child expenses
    \item Find a new pool or workers - foster homes - lose the stigma of growing up in a foster home
    \item Can we help or can government help in lower certain living costs
\end{itemize}

Although Canada has an older population, the indigenous population is very young there are more indigenous people under the age of 15 then the rest of Canada

Of the solutions mentioned, which do you think would work the best in the foreseeable future

How many people immigrate into Canada each year? ~450,000 people (Largely a federal issue)

Diversity (Thought and Decision making)

\begin{itemize}
    \item Where are some area where we would like to see diversity?
    \begin{itemize}
        \item Board of directors/executives - how are we doing so far? - doing well so far but traditional industries are slow to move. There should be a pressure campaign from outside sources to change the inside of certain companies. Who has this power?
        \begin{itemize}
            \item Warren Buffet
            \item Human right activists
            \item The federal government
            \item Consumers
            \item Institutional investors - Insurance companies, Banks (TD, CIBC, RBC, BMO, Scotia, National Bank), Investment banks (Goldman Sachs, JP Morgan), Pension funds - The only way these institutions can influence change is if they are all together
        \end{itemize}
        \item Within an organization, we managers need to provide 3 variables to help push along diversity. People of diversity need to have opportunities to
        \begin{itemize}
            \item Gain power
            \item Gain influence
            \item Have growth opportunities
        \end{itemize}
        \item What keeps the status from changing, what is making it so hard?
        \begin{itemize}
            \item Not enough risk takers, it can be time consuming and expensive to make diversity happen.
            \item Traditional views are harder to change - Bombardier
            \item People who are in power don't like to give it up
        \end{itemize}
    \end{itemize}
\end{itemize}

% Describe the glass ceiling 

% Does the current diversity quota system work?

% What role do levels of government play to encourage or discourage diversity

% How can you as a consumer help

% Find one article about diversity and summarize in two paragraphs




% Businesses will have a competitive advantage with diversity

% Business Case

% Bi-directional communication

% Diversity counsil


% Train, communicate & educate

% show people business case 

% can you go to far?

How does management and climate change relate or connect?

\begin{itemize}
    \item Monitor carbon emissions - introduce alternative energy solutions
    \item Preservation and conservation of the biodiversity that exists in this country and beyond
    \item Make wiser decisions about waste management, export of waste to other countries and disposing of waste away from oceans and lakes
    \item Find supplies and resource that are extracted 
    \item Rules and laws and taxes can encourage or discourage certain strategies around climate change.
\end{itemize}

\textbf{Orsted}

A company which switched gears and went from natural gas to wind energy

%TODO: Create mindmap

Test 2:
    Globalization
    3 C's
    Workplace trends

\section{Chapter 3}

Ethics in management

Ethics in business management plays a significant role in decision making, planning, creating and innovating

\begin{itemize}
    \item Business morals - they will be different from one company to the next
    \item Business beliefs - values
    \item Business culture - inclusiveness, creation, risk
\end{itemize}

Ethics is the study of what is right and wrong but it really depends on one's perspective

Companies that operate ethically
\begin{itemize}
    \item Lush beauty - not hurting animals
\end{itemize}


Let's identify some ways of making companies operate in a more ethical manner - what are some strategies?
\begin{itemize}
    \item Implement rules around working conditions (many of these global companies outsource the manufacturing and therefore are not liable if issues with working conditions are bad - Apple is in a contract with Foxconn)
    \item Vote with your dollars
    \item Presure them from the outside and the inside - investors of these companies can vote and make their voices heard
    \item Eliminate staff or management that is not willing to change or is acting unethically - clean slate
\end{itemize}

What is the most common site you use for social media - Instagram - is owned by Facebook

Is instagram an ethical company?

Yes:
\begin{itemize}
    \item Brings people together
    \item Supportive of LGBTQ, cyber-bullying strategies, small businesses and connecting
\end{itemize}

No:
\begin{itemize}
    \item Superficial - Women's body
    \item Excessive amounts of information
    \item Fear of missing out
    \item Addictive, Misinformation
\end{itemize}

Is the Humane Society ethical?

Yes?
    They provide a shelter for animals and gives them an opportunity to live a better life, I never really have heard of any scandals, so looks good to me.


Why should companies not act ethically responsibly?

\begin{itemize}
    \item Profit driven - without profits you can't run a business - one track mind
    \item Depends on the industry - resource extraction
    \item Really many large companies must be accountable to their investors - banks, investment banks, pension funds
    \item Some companies are in the dark about their connections suppliers, and other subsidiaries
\end{itemize}

What does ethical leadership look like?

\begin{itemize}
    \item To appeal investors
    \item Establish good reputations - marketing - have positive feelings about your brand
    \item To gain government support
    \item Companies can make more money by active ethically - business advantage to 
    \item Companies to recognize that they are a part of the community and are not isolated
\end{itemize}

One of the ways to spur ethical action inside a company is by being or becoming a whistleblower. A person who despite the risks and challenges, decides to publicly try and change the direction of a company. Many companies are hostile to whistleblowers and whistleblowers are not often protected and can easily be fired

What are some things that whistleblowers blow the whistle at?

\begin{itemize}
    \item Corruption
    \item Human rights violations
    \item Animal Cruelty
    \item Workplace injustice - discrimination
    \item Environmental footprint
\end{itemize}

Let's list some benefits of whistleblowing

\begin{itemize}
    \item Informs the public 
    \item Creates actions against the company - change
    \item Holds companies accountable to their actions
    \item Shines a light on a business or government
    \item It protects and defends people who might not be able to do it themselves
    \item Makes companies change strategies and direction
    \item List some of the downsides to whistleblowing
\end{itemize}

whistleblowing consequences

\begin{itemize}
    \item Lose your job - lose your reputation - lose your brand
    \item Create a culture of fear - people looking over their backs
    \item A company lose profit and possibly shut down
\end{itemize}

How does whistleblowing enhance our democracy?

\begin{itemize}
    \item Create change
    \item Gives people a voice who don't ordinarily have one
    \item Trying to establish policy between equity and equality
    \item Helps enhance our systems of justice
    \item It shines a spotlight into dark areas of companies and governments
\end{itemize}

How can managers encourage a whistle blowing culture

\begin{itemize}
    \item Inform employers to make sure they are receptive to criticism
    \item Have a cultural philosophy that encourages whistle blowing
    \item Normalize whistle blowing
\end{itemize}

CSR - Corporate social responsibility - what does this entail? Not only profit driven but advancing society - achieving goals of the community - restaurants that contribute free meals to the local church or another venue for people who are hungry - a company that has a charitable aspect to it - it's important to keep the for profit part of your company separate from the charitable part of the company

Who engage in CSR?

\begin{itemize}
    \item Brand
    \item The company will be seen as ethical or community engaged
    \item Business case - more profits
    \item Investors really want organizations to be CSR oriented
    \item Sustainable - like last longer
\end{itemize}

The first way that has become popular to make corporations become more CSR oriented is the use of a boycott - makes people or consumers actively stop buying from a certain company and try to stop others from doing so as well


Do boycotts work and if they work how effective are they?

If they are effective then what is a better solution

\begin{itemize}
    \item Hurt company profits
    \item Social media plays a role
    \item More effective for small companies
    \item Depth of pressure of tactics
    \item Rarely works
    \item Business Case
    \item Must be consistent
    \item Can hurt the economy
    \item Boycotts can become normal
\end{itemize}

I tend to think that boycotts mostly don't work. I think it's better to collaborate to change a company from the inside, to change laws and enforce laws and not create more division and de-escalating - better for corporations and consumers to meet in the middle.

The pay of chief executive officers (CEO's)
\begin{itemize}
    \item These are people that manage large companies - it's a CSR issue because what employees paid - what does a CEO do? 
    \item 1. Determine pay of employees
    \item 2. Communicating on behalf of the company (face of the company)
    \item 3. Organizing and participating in board meetings
    \item 4. Small and big picture strategies
    \item 5. Take a lot of the scrutiny of the company
    \item 6. Determine the level of risk for a company
    \item 7. responsibility for all those involved
    \item 8. Motivate people to do things and to sell things
    \item 9. Make transactions easy for people buying the product or service
    \item 10. Very flexible - pivot in new directions - bank CEO's have shifted into more digital space
\end{itemize}

CEO's - Susan Wojcicki, Elon Musk, Satya Nadella, Lisa Su, Phil Knight, Jeff Bezos, Mark Zuckerberg

Significant points from McDonald's video

\begin{itemize}
    \item CEO's make much more money compared to on the ground employees
    \item CEO pay is one segment of the business - some people would argue that we should focus less on CEO pay and more about what the business is offering
    \item CEO's have certain qualities that other people don't have - justify their pay
    \item People that influence the decisions of the company can determine if the CEO should receive a raise or a pay cut
    \item It depends on the culture of the company and what it's goals are - one CEO that tries to keep the gap between employee earning and CEO earning is the CEO of Whole Foods - top heavy vs. bottom heavy
\end{itemize}

Special segment to Mark Zuckerberg - the special role that a CEO like him plays - the responsibility of it all (Facebook, Instagram, What's app)

\begin{itemize}
    \item The control of what we see, hear and listen to (the news)
    \item Monopoly power - dominance over free speech, elections
    \item Has the power to bring people together but also to divide people - we want society to exist in some sort of people
    \item Sway people's opinions about things that have happened in history and currently (Is trying to now take down misinformation about the holocaust)
    \item Create their own digital currency (Libra)
    \item Entrusted with so much personal data and personal history
\end{itemize}


    In general, do you think CEO's are earning too much money?

    Yes on one side
    \begin{itemize}
        \item CEO's continue to earn more each year while workers do not
        \item Leaves a large gap between those CEO's and workers
        \item Given larger wages, CEO's have more opportunities to evade taxes or pay less taxes
    \end{itemize}

    No on one side
    \begin{itemize}
        \item They earn the money due to their hard work
        \item CEO's are responsible for managing the continued success of the company
        \item CEO's put their work life first and not many people are willing to do that
        \item Pays more in taxes - they contribute to they economy
    \end{itemize}

    Offer 3 conclusions and then one opinion stating yes or no

\subsection{Test}
\begin{itemize}
    \item Ethics
    \item Whistle-blowing
    \item CSR - boycotts, CEO compensation/pay, Orsted
    \item Ethical investing (Facebook - the special responsibility of someone like Mark Zuckerberg - Instagram)
    \item 44 Marks - Case study \& questions
\end{itemize}

\section{Unit 4}

It's up to us as managers to help determine what our competitive advantage will be. A competitive advantage is one thing or a couple  of things your business has that another business does not have. It's the main reason why a person buys from you and not another business

The key is to try and establish sustainable competitive advantage. A competitive advantage can change over time. It's a moving piece.

Companies that have a competitive advantage and what that competitive advantage

\begin{itemize}
    \item Amazon - low prices, market share, shipping everywhere, brand, convenience, \textbf{logistics}
    \item Netflix - first to the market, lots of options of entertainment
    \item Drums and Flats - bar - Ave \& Wilson - live bands, chicken wings, convenience (location)
\end{itemize}

Is a place like this, over time can change their competitive advantage during the pandemic, get into delivery but not necessarily use the door delivery companies - social media presence - keep enticing people to come back - a restaurant that has a ghost kitchen - extend your food service by focusing purely on delivery

What is your competitive advantage 
What is Mackenzie's Competitive advantage
\begin{itemize}
    \item MACS
    \item Academic
    \item Highly ranked
    \item Next to subway - Yorkdale mall
    \item Reputation - strong history
\end{itemize}

Uber represents a company that has a moving competitive advantage. At first, they were a technology company, transporting people all over. Then they morphed into a Data Company. Location, where you are going, phone number, route, credit card, debit card. - sell that data to advertisers - advertisers can target you - now they are changing again into autonomous driving.

User is harmful to the environment - excess cars on the roads - there are parts of Uber that are environmentally friendly (ride sharing, Uber green) - Relates back to ethical investing

Economic systems

\begin{enumerate}
    \item Monopoly - one seller in the market - control prices for what consumer pay - barriers to enter the market are quite high - market share is really high +90\% - Google, LCBO, The Beer Store, Pay-Pal, TTC - some companies operate as a Natural Monopoly - this means the government determine that it would be best if only one company sold something - Waste management - Green For Life
\end{enumerate}

Monopolies are good for shareholder but not really good for consumers

Oligopoly - a few sellers - or a few more - pretty much own the entire market - price makers - barriers to compete with these companies is high - better for shareholders but not really good for consumers

\begin{enumerate}
    \item Telecommunications - Rogers, Bell, Telus, Vodafone
    \item ISP - Rogers, Bell
    \item Phone companies - Apple, Samsung, Nokia, Android
    \item Grocery Store - Metro, Loblaws, Costco, Sobeys
    \item Airlines - Air Canada, West Jet, Sunwing
    \item Banks - CIBC, RBC, TD, BMO, Scotia Bank, National Bank, Laurentian
\end{enumerate}

Main point about the article:

A merger is when two or more companies combine - one of the things that can keep workers' wages down - reduces competition, keep shareholders happy but keep consumers unhappy

Prime Minister -> Justin Trudeau

Ontario Premier - Ford
Quebec - Legault (I chose this)


\begin{enumerate}
    \item Pandemic
    \item Economy
    \item Environment
    \item Transportation
    \item Affordable housing
\end{enumerate}

As part of your Culminating, a SWOT is require. A SWOT analysis is an examination into your company and outside your company. Each letter represents something:

\begin{itemize}
    \item Strength - Strengths of a company - A quality workforce, brand loyalty, first mover advantage, location (Assets are greater than liabilities, free cash flow positive, capital for daily expenses and long term expenses) is supportive of mental health- internal elements of the organization - emphasize your strengths even though you or a business will have a weaknesses. 
    \item Weaknesses - Internal - mismanagement of funds, lack of diversity, resource limitations (workers, skilled trade, money, time), young company, not having clear objectives, not having a good hiring policy, not adapting to technology
    \item Opportunities - External - Investors, Celebrations, Social Media, Taking advantage of trends, Mentorship, Expansion, Merging, Acquisitions - Revolve around your growing market share, growing profits, expanding your service or product
    \item Threats - External - Competition, Regulations from Government (Red Tape), Market Saturation (Too many companies in the same space), Climate change, Lawsuits or legal issues (is the workplace safe?), Uncertainty (tangles world makes this so prevalent) - Politically, Pandemic, Unemployment Rate, Tension
\end{itemize}

Conclusions about SWOT - don't get too caught up in it, weaknesses can become strengths, strengths can becomes weaknesses, Opportunities can become threats and threats can become opportunities - moving documents

Complete a brief SWOT analysis for the city of Toronto

\begin{tabular}{|c|c|c|c|}
    Strength & High diversity & Diverse sectors & Tourism asset \\
    \hline
    Weaknesses & High housing market & Reliance on US & Education\\
    \hline
    Opportunities & Growing market & Multiple services & Transportation\\
    \hline
    Threats & Canadian Dollar & Aging workforce & Cost of living\\
    \hline
\end{tabular}

Another acronym that we will learn now is PEST

Political - who is in power, how do you vote for people, what type of power is it (democracy, authority) - the political system directs the business culture that a culture has 

Economic - What type of economy is in the country (market based economy, state based economy, or a mixture of the two), what and who determines prices of products, is the economy more service (digital, knowledge) based or product (resource) based

Societal - What does society look like, what are its values, its interests, its needs

Technology - infrastructure, speed, reliability, widely used, digital literacy, rural vs urban divide

St. Mikes College a couple years ago

Whats the situation?

Bullying incidents of a horrible nature - involving people that were students at the school 

Let's list the important players - all the types of people involved in this situation - directly or indirectly - stakeholders

\begin{itemize}
    \item The players (Football)
    \item The principal
    \item The victims
    \item Entire student body
    \item Parents
    \item Community
    \item Court system
    \item Faculty
    \item Board of directors
    \item Media
    \item Police officers
    \item Alumni
\end{itemize}

From a management perspective, how can we create a culture where this does not happen?

\begin{itemize}
    \item A more open school society - more acceptance of people - especially the younger students
    \item Better supervision - interactive
    \item Coaches play a role here - role models - have a responsibility to set the tone
\end{itemize}

What makes work meaningful? We are not talking from the employee standpoint we are talking about it from the management standpoint - how can managers make work meaningful for their employees

\begin{itemize}
    \item Flexibility - hours of operation, technology helps, encourage people to do other things besides work
    \item Encourage peer to peer work relationships - collaboration - people want to collaborate for the most part
    \item Let or encourage people to be creative - innovative - experiment - explore - observe
    \item Community centric - positive impact on the community - ethical
    \item Personal recognition - pay raise, awards, promotions, small signs of recognition are important too
\end{itemize}

% There is some research that shows the more people engage with technology the less engaged they 

How can managers hire and retain quality people?

\begin{itemize}
    \item Incentives - pay increase, benefits (dental, vision, therapy, vacation, childcare)
    \item Creating stability and less uncertainty - long term contracts can be helpful (tenure)
    \item Promotion opportunities
    \item Encourage people to innovate and take risks and fail
    \item No need to have a traditional hiring process - have an innovative hiring process
    \item A strong referral process - have a trust between manager and employee
\end{itemize}

None of these are easy to achieve

Environmental, social and corporate governance (ESG)

Managers are being steered to conduct business with an ESG mindset

\begin{itemize}
    \item Environmental - Climate change, pollution control, not depleting resources, reduce use of plastic, conservation, more renewable focussed energy goals, protecting lakes, oceans and parks - be careful about green washing
    \item Social - CSR, Values, Attitudes, Reputation, Image of the company, how progressive is the company, diversity targets, health and safety, trends (metoo movement, BLM)
    \item Governance - who gets to control things, who sits on the Board of DIrectors, who get promoted to management, who gets to make decisions, executive pay
\end{itemize}

The federal government and its ESG initiatives

\begin{itemize}
    \item E - Carbon tax - a tax on companies that emit carbon into the air - as a consumer you actually will earn a rebate if you pay the carbon tax for instance when you fill up your car with gas. They are attempting to pass laws that limit single use plastic. Make efforts to save Right Whales in the St. Lawrence Seaway
    \item S - Preventing conversion therapy for those people in the LGBTQ, a commitment to more females and BIPOC to run for leadership and represent communities in Ottawa. Passed a law that lets people who are terminally ill to request an assisted death
    \item G - Trudeau will force people to resign if he feels they are not working unity, cabinet shuffles
\end{itemize}

Write three points for each letter in the ESG - Tim Hortons's

\begin{itemize}
    \item E - Redesign their cups for be more spill resistant - Roll up the rim to win more environmentally friendly
    \item E - Animal welfare - Animal care for those within the supply chain
    \item E - Reducing GHG
    \item S - Camp Day
    \item S - Smile cookie
    \item S - TimBits Program, Festive foods (Hockey, Canada day)
    \item S - A reputation for not wanting to pay workers the Ontario minimum wage rate
    \item G - Franchisee model system - there is a Franchisor that is there to assist the local Franchisee's - the Franchisor provides lots of support, funds, training, digital help to Franchisee. Tends to be against unions but some Franchisee have set one up. It's owned by a much bigger international company called Restaurant Brand International (RBI)
\end{itemize}

Union / Unionization - why do unions exist?
\begin{itemize}
    \item Give employees rights and a voice - fair pay and benefits
    \item Protect employee jobs - give employees stability and certainty - does not apply to all sectors
    \item Coordination of worker rights
    \item Empower people who are traditionally vulnerable (women and BIPOC)
\end{itemize}

\begin{itemize}
    \item Disadvantages - Corporations often not to like unions because corporations want to be in power
    \item Part of your employee salary is deducted to pay union dues
    \item From a management perspective its so difficult to let go people that are not being productive
    \item Advantages - Benefits (physiotherapy)
    \item Almost eliminates the precariousness of the employee
    \item Puts employees into the middle class group
    \item Gives employees a voice
    \item Provides greater economic growth and stability
\end{itemize}

Why is unionization declining in most parts of NA and can this trend be reverse or does it not matter?

\begin{itemize}
    \item Positives and negatives - the positive is that unions try and protect jobs but the negatives are also plenty (less incentives for workers to push themselves to become more 'productive')
    \item Precarious workforces may try and establish union membership but this goal is lofty and could be unrealistic
    \item So much depends on the strength of the union - traditionally teachers in Ontario have a strong union while teachers in Alberta have a weaker union
    \item Unions have proven to be economically beneficial (create employment certainty) however it won't make people necessarily economically 'wealthy' (Provides economic stability rather than growth)
    \item Always going to be this battle between corporate interests and employee interests
\end{itemize}

Some thoughts and summary points and analysis of Ajay Banga (Mastercard)

\begin{itemize}
    \item Prioritizes workers - decided against laying off people during the pandemic
    \item Mr. Banga has a long term mindset instead of a short term mindset - 3 year mindset instead of a three month mindset.
    \item Wide range of experiences have helped shape his perspective 
    \item Believes CEO pay is acceptable as long as it is connected to the success of the company or investors in the company
    \item Good example of CSR - leads with empathy
\end{itemize}

Where are we headed - to understanding the differences and similarities between management and leadership

List some characteristics of management or managers
\begin{itemize}
    \item Delegating responsibilities to others
    \item A person who is open to suggestions
    \item A person who makes decisions that show diversity in thought and decision making
    \item A focus on the more day to day business operations - short term focussed
\end{itemize}

Examples of managers - John Tory (Mayor of Toronto), Mr Johnson, Lifeguard, Vice Principal, Teachers

Characteristics of leaders or leadership

\begin{itemize}
    \item Long term vision
    \item Overall focus on the greater good and not necessarily on the day to day transactions
    \item Able to persuade people to do thing
    \item Able to connect with people
    \item Decisions makers - not always making popular decisions
    \item Selfless - a person who puts others before them
\end{itemize}

Examples of leaders - Mr Johnson, Tim Cook, Greta Thunberg, Justin Trudeau, Erin O'Toole, Jagmeet Singh, Annamie Paul

Trends in worldwide leadership

\begin{itemize}
    \item Diversity is increasing but the pace is slow
    \item Some leaders are showing empathy (Jacinda Ardern) while other leaders have shown much less empathy - Kamala Harris fits the mold of empathy and times of no empathy
    \item Communication - is honesty important - from a leadership standpoint, absolutely
    \item A leader who listens to the people (the majority and the minority should be listened too)
    \item Is leadership still important or has social media dimished the role of leaders - has really assisted their message but it can also taint the message
    \item Are leaders around the world getting along - some are (Trudeau) while others are not (Trump)
\end{itemize}

Do this on your own - Draw a picture of a person that is a leader to you - that looks like a leader to you.



\subsection{Test}
Competitive advantages
SWOT
PEST
Meaningful work - how to hire and retain employees of quality
St. Mikes College
Unionization
ESG

Important to note for SWOT strengths can become weaknesses and opportunities can become threats and vice versa

Culminating due class after test (Nov 17 in class)





\section{Culminating}
Company I chose: Canada Computers

20\% of Mark

Two Sheets on one side, two sheets on the other.

11 or 10.5 font

Create an organization or analyse a current organization

\begin{enumerate}
    \item Give general description of the organization
    \item What is their mission statement? -> What does it focus on?
    \item Describe the product or service
    \item Market analysis -> study the industry, trends, competition
    \item SWOT analysis - Strength, Weaknesses, Opportunities, Threats.
    \item What are some policies and procedures
    \item Describe the organization's method of control
    \item Describe the structure of the organization
    \item How does the organization attract quality people
    \item Describe the leadership of the organization
    \item How is conflict managed
    \item How is the organization creative and innovative
    \item Describe the compensation of the organization
    \item Predict the future of the company - Financial stand point - Sustainable standpoint (CSR)
\end{enumerate}

\begin{enumerate}
    \item Canada Computers is a store which provides niche products which you won't find in large computer stores. It's market is towards the tech-savvy or various enthusiasts.    
    \item The retailer is dedicated to offering the best technology, advice, and service that enhances peoples’ lives.
\end{enumerate}


Styles or types of leadership

Authoritarian - one person who makes the decisions - rely on certain friends or family for help but for most past it's one person - persuade by threat - decisions can be made faster provides a lot of control to management - China, Vietnam, Russia, NK - companies - huawei, wal-mart

Laissez faire - hands off approach of management - encourage people to make decisions on their own - responsibility falls to employees - parts of the usa, hong kong, singapore, dubai/uae - some companies in the usa and britian that are more employee centric then menagement centric - google 

Democratic - a relationship or a trust between management and employees - making decisions together - hard to make everyone happy - lots of challenges but there is lots of reason to be democratic because profits tend to flow to these companies - employees will feel engaged. Canada, France, Scotland. Most companies operate this way

How can we measure how good an employer, manager or leader is? A few different criteria

\begin{itemize}
    \item Physical workplace
    \item Work atmosphere
    \item Benefits (family, health, financial)
    \item Vacation time - time off
    \item Employee Communications
    \item How well does management perform
    \item Training and skills and development
    \item Community involvement
\end{itemize}

Best buy

Bank of Canada

Women in Capital Markets

Myth is women are less ambitious then men, in fact they are both equally ambitious - myth that women want more work like balance then men - myth, lack of qualified of women then men

Compensation - benchmarks, transparent to how to achieve that level of compensation, including bonuses - opportunities can be skewed towards men - solution - encouraging both genders

Black women feel especially targeted - change in culture, leadership, mentorship, break in traditional chain - Asian women are more optimistic about the promotion opportunities

Equal treatment - gaps between people - men feel they are being treated equally while other groups are not - BIPOC feels worse than others - 

Equal Opportunities - men agreed, other groups not so much - within the industry - gaps exist between genders (buy side and sell side) - gender can be a real disadvantage - groups outside the majority feel the most inequity

Equal pay - differences - beliefs differ - perception is important

Safety and belonging - some people hide their personal lives - both men and women - depends on seniority - less productive, 

% 1.  Give general description of the organization
%     Canada Computers is a store which provides niche products which you won't find in large computer stores. It's market is towards the tech-savvy or various enthusiasts.    
% 2.  What is their mission statement?  - What does it focus on?
%     The retailer is dedicated to offering the best technology, advice, and service that enhances peoples’ lives.
% 3.  Describe the product or service
%     Canada Computers provide different products and services, products that you would and would not find in a big box store, from cpus to printers, tvs, cameras, etc. Canada Computers provides products from novices to enthusiasts. Canada Computers also provide technology related services, from phone / pc repairs to troubleshooting to home theater installation.
% 4.  Market analysis - study the industry, trends, competition
%     Canada Computers' focus in the industry is largely focused towards PC enthusiasts, but also provides services for businesses. In term of trends, I assume there will be a gradual increase in this industry towards enthusiasts. This is since people are being introduced to technology every day, and of those, some will become enthusiasts. I also think social media also helps this industry, channels such as LinusTechTips, JayzTwoCents provide a approachable way into the pc world and bring you up to speed on the latest news, this is special, because it addicting and engaging, and you come out smarter than before. Canada Computers does have competition, although it completely exists online, this gives Canada computers a big competitive advantage as it is the only store which has a physical store. This is a competitive advantage as consumers would rather buy from an online store for convenience, if a return was needed, you could return or trade for something else within the hour with Canada Computers, while online stores would require more time and effort.
% 5.  SWOT analysis - Strength, Weaknesses, Opportunities, Threats.
%     Physical store, Multitude of services, Has products you would not find in big box stores
%     Not as globalized as some competitors, Bad management, COVID
%     More personlized services, IPO, Globalization (More stores)
%     Easy market for existing competitors to enter, Large competitors, Fluctuating market for parts (Ram prices), tarrifs, taxes, anything that can cost the company money
% 6.  What are some policies and procedures
% 	Call the company
% 	https://www.canadacomputers.com/policies.php?page=policies-privacy
% 	https://www.powerdms.com/blog/corporate-policies-procedures/
% 	Vacation days
% 	Sick days (2)
% 	Benefits
% 	Union
% 	Equal Opprotunity
% 	Workplace safety
% 	How do you motivate employees
% 	What makes you standout from companies
% 	Breaks
% 	Company culture
% 7.  Describe the organization’s method of control
% 	How do you keep employees safe and accountable, and ensure quality and consistency
% 	Training
% 		How do you keep your services consistent (ensure quality)
% 	Budget 
% 	Employee control
% 		Training
% 		Commission on warranty
% 	Profit Driven
% 	Inventory control
% 		LIFO (Sell older products so you waste less money when a new product comes in)
% 		Establish par levels (Maintain inventory)
% 		Manage supplier relationship (Very important)
% 		Fine tune your forecasting
% 		Audit your stock
% 	Call the company
% 8.  Describe the structure of the organization
% 	HR
% 	Store/Retail
% 	Customer Service
% 	Logistics (Category Manager)
% 	Accounting
% 	Social Media
% 	Merchandiser
% 	IT
% 	eCommerce
% 	(Head office) -> (District manager) -> (Store manager)


% 	Call the company
% 9.  How does the organization attract quality people
% The way Canada Computers attract quality people are with benefits, promotion opprotunities, and commission for certain sales. 

% 	Benefits
% 	Promotion Opprotunities
% 	Commission
% 	Call the company
% 10.  Describe the leadership of the organization

% 	Authoritarian (based of indeed reviews by former employees)
% 	Call the company
% 11.  How is conflict managed
% With the average company, conflict management often involves finding areas of potential conflict and resolving them before happen, report conflict to the manager, or anger management sessions. 

% 	Get info from employee review
% 	default to ontario standards
% 	Call the company
% 12.  How is the organization creative and innovative
% Looking at Canada Computers' press releases, the organization is creative and innovative by being accomadating to the customers, accepting WeChat Pay, Alipay, working with local businesses to bring new products to consumers, offering exclusive products.


% 	"we offer the niche products you won't find in the big box stores"
% 	https://www.canadacomputers.com/press_releases.php
% 	Call the company
% 13.  Describe the compensation of the organization



% 	# Hourly, Salary, Commission, Bonuses
% 	Salary
% 	Commission
% 	Call the company
% 14.  Predict the future of the company - Financial stand point - Sustainable standpoint (CSR)
% 	Refer to 4 and call the company and ask them themselves

% Sources: linkedin, indeed, yelp

% Canada Computers reward card - customer loyalty

% Ask what it has done during COVID
% https://www.canadacomputers.com/covid_19.php

% How do you maintain relationships with brands?
% Inventory control


% Look at job postings


% We were given a task to choose a company or oganization to analyse, and I choose Canada Computers. 

% 	Canada Computers is an electronic store, founded in 1991 by Gordon Chan. It houses stores across Ontario, Quebec, British Columbia and Nova Scotia and also has an online store, but a large majority of stores are located within the GTA. In 2018 Canada Computers had over 1000 employees in 35 locations and it is a first choice to PC enthusiasts and gamers. Canada Computers' mission statement says they are dedicated to offering the best technology, advice, and service that enhances peoples’ lives. They sell a variety of products and services and keep up with today's trends. From the outside one might relate Canada Computers to a Best Buy, but I can assure you they are not the same, Canada Computers' explicitly say that they themselves, "offer the niche products you won't find in the big box stores. This is what makes Canada Computers & Electronics stand out. We've got it all and we're proud of it." They do provide traditional products such as, laptops, pcs, tvs, cameras, printers, and other items you would find in a Best Buy but what makes them a first choice for gamers is their wide variety pc components, cpus, rams, motherboards, gpus, fans, keyboards, mouses, headphones, earbuds, products tailored to their customers and things you would not be to find in any physical store. As of now Canada Computers' competition has changed over the years, in the past Canada Computers had physical competition with other stores, such as NCIX, TigerDirect, and Memory Express. NCIX is now bankrupt, TigerDirect now only has an online store, and Memory Express locations have little overlap with Canada Computer locations. As of now, the only competition Canada Computers does have are all online stores such as Amazon, Newegg, TigerDirect, Best Buy all compete with Canada Computers in the same market. Even though Canada Computers' consumers are often enthusiasts, they do market to those who are a novice when it comes to technology, providing customer service in-store and services online such as installation, repair, backup data recovery, virus removal, driver installation, home theatre installation, security installation and a variety of tv delivery services. 
% 	The industry which Canada Computers is in is largely focused towards pc enthusiasts and gamers who would buy peripherals or pc components. The industry which Canada Computers is in also encapsulates other industries, more specifically the cpu, ram, storage, gpu and motherboard industry, all of which have frequent innovation and creation, meaning there is always something new, something faster, something better that is being released. In terms of trends, I think there will be a gradual increase in this industry because people are being introduced to technology every day. 
% 	As technology advances, people will become more and more integrated into technology, and of those, some will become enthusiasts. I also believe that social media will contribute to the gradual trend as it is really addicting. I feel that there is something special with social media and technology, channels such as LinusTechTips provide an approachable way into the pc world, bringing you up to speed on the latest news and teaching you the ins and outs of a pc in a very engaging manner. I especially relate to this because this was how I became an enthusiast. 
% 	As said before, Canada Computers has competition, and some of its main competitors are Amazon, Newegg and Best Buy. Look at each store, they all stay up to date on the newest products and have a wide variety of products for its categories. Online stores often compete with others through their pricing. Looking at the pricing history for various products, we can see competitors frequently change their prices to compete against their competitor.
% 	As much as we know about Canada Computers now, it is a good idea to do a SWOT analysis. A SWOT analysis is a great tool for analysing the ins and outs of a company and understanding its current position and what they might face in the future.
% 	Looking at the strengths of Canada Computers, having a physical store is a big strength. As all the competitors are online stores, this provides Canada Computers a competitive advantage, it's a physical store you can go to. For a consumer, this could be the reason why they choose Canada Computers over its competitor, as it's less time consuming and more straight forward. As a consumer, I can find what I need from Canada Computers on the same day, if I need to return the item, I can go to their store and ask them for a refund in person. In contrast, if I buy something from Amazon, it'll take me longer to get it, I would have spent a few hours on customer service if I needed to return it, and I would have to wait even longer to get a replacement. You're there when you buy it, you know exactly what you are getting when you buy in-store. Another strength is that Canada Computers provides a multitude of services, some of which are not available to competitors, such as Best Buy, and are usually cheaper.
% 	Like any company, Canada Computers also has its weaknesses, one of which is that they are not as globalized as their competitors. So if there is any competition with Canada Computers and a competitor, Canada Computers will surely lose, not being as globalized as other competitors also mean that Canada Computers cannot take potential profits from markets in other cities. As Canada Computers is a physical store, one of their weaknesses is the fact that they have been impacted by the pandemic, this creates uncertainty as they may lose money through loans, rent, electricity as they wait for certainty. According to reviews by former employees, many have complained about bad management within all levels, this creates disloyalty, uncertainty, you lose out on quality employees and give the company a bad image, this hurts profits for the store.
% 	As we saw, Canada Computers has many weaknesses, but with that comes opportunities. One big opportunity for any private company like Canada Computers is an initial public offering, this gives Canada Computers funds and publicity. Funds to expand their business and publicity to attract more customers. Even without an IPO, expanding is a great opportunity for Canada Computers as there are many markets in different cities which do not have a physical store which markets to PC enthusiasts and gamers. A more creative opportunity is to have a more personalized service. The reason being that is since many people who are new to computers and want to build one would often buy the parts and build it themselves, but often will misconfigure some settings, break a component or forget a key piece needed to boot up the pc. An opportunity for Canada Computers to make a profit is to have a service where someone walks them through building a pc, gives recommendations of the best parts to buy, what will fit in your budget, and will help you build your pc.
% 	With any opportunity comes threats. One such threat is a larger competitor mimicking Canada Computers' physical stores. As mentioned before, if there is any competition with Canada Computers and a competitor, Canada Computers will surely lose and in this case, it rings true. Another threat is that Canada Computers has contracts with various tech companies around the world, if global relations become strained, taxes or tariffs might be imposed which can hurt profits for Canada Computers.
% 	Lastly, it is worth mentioning that when doing a SWOT analysis strengths can become weaknesses, opportunities can become threats and vice versa. Take a weakness for example, although Canada Computers is not as globalized as their competitors, they mean that they are able to focus and provide a better service to a smaller area and develop loyal customers.
% 	I would like to mention that most of what is being said are based on reviews by former employees. I called Canada Computers, but there was no answer.
% 	As I was able to obtain little information of Canada Computers' policies and procedures, so I had to make some deductions and educated guesses. Canada Computers, being a relatively small company, would most likely have policies and procedures similar to other small companies which I would guess the minimum required for employees. Based on this and reviews from former employees, Canada Computers' policies and procedures consist of the following, as a sales representative, you are entitled to two weeks vacation time, two sick days, basic benefits, and minimum training. I could find no information on unions, workplace safety, equal opportunity, whistleblowing or breaks, so I assume there are no unions, workplace safety would follow OHSA, policy would want equal opportunity, but it would be rarely enforced, manager are open to criticism and have a philosophy which encourages whistleblowing, and break are following the Ontario standards.
% 	Similar to the paragraph before, I will make inferences and educated guesses to this company's method of control due to insufficient information. From what we do know, Sales representatives have a responsibility to maintain the store, that is keep the shelves stocked, maintain inventory, or ensure quality among employees. From this we can inference Canada Computers uses a top-down approach to control as many former employees have mentioned a one sidedness to management.
% 	The following are inferences and educated guesses due to insufficient information. The structure of an organization is important to understand as indicated the roles and responsibilities which certain people have and according to Canada Computers' linkedin account, their structure is a functional structure, where the firm is divided into departments such as, human resources, store and retail, customer service, logistics, accounting, merchandiser, IT, and eCommerce.
% 	From what information I was able to find, Canada Computers provides common perks in order to attract quality people, these include benefits, promotion opportunities, and quality co-workers. The only quality which stands out for Canada Computers is that a sales representative is able to gain commission for selling the customer warranty.
% 	Based on reviews from indeed.ca, Canada Computers uses an authoritarian leadership, where sales representatives answer to the manager and the direction of the store is often based on what the manager wants to do. This gives managers full creative control, but is evident by reviews it leaves the sales representative in fear of their job.
% 	As I was not able to find any information related to conflict management, looking at the average company, companies often want to be proactive when it comes to conflict rather than reactive, so companies often implement techniques such as creating a productive work environment to make it clear when will and will not be tolerated, identifying and addressing hot topics among employees to take care of conflict in a controlled manner.
% 	As I was not able to contact anyone who works at Canada Computers, I thought the next best thing was to look at the press releases and infer from that. My logic is that whenever a company is creative and innovative, they would like to tell the world, and a press release is one way to do that. Judging by their press releases, Canada Computers is creative and innovative by thinking about the customer, adding new methods of payment to make it easier to pay, adding products that would interest the consumer, and by having custom deals and discounts.
% 	Based on reviews from former sales representatives, the compensation which sales representatives receive are a salary and commission on selling warranty to customers. Sales representatives also receive employee discounts, and benefits.
% 	Given all the analysis we have done, I feel fine predicting that Canada Computers will have a fine future, so long they are able to fix their poor management. Currently, the industry has a large amount of competition but I think Canada Computers has many loyal customers within the GTA. Also, Canada Computers' success ties to the success of other companies, specifically the cpu, ram, storage, gpu and motherboard industry, and as I said before, new innovations and products are frequently released, so long as Canada Computers is able to maintain their competitive advantage, they will continue to succeed. From a sustainability standpoint, Canada Computers is a great option for PC enthusiasts and one of the best options out there to get into building a pc.










% Based off of reviews seen on indeed.ca, Best Buy's physical work often include comunicating with customers, working the floor and maintaining inventory. Their work environment 

% Based off of reviews and questions answered on indeed.ca, we are able to get a general idea for each criteria.
% Physical Work:
% 	As a sales representative, you're in the store helping customers, and maintaining inventory. There isn't any competition so employees works well together and give the sales culture a good name.
% Work Environment:
% 	As a sales representative, the work environment is fantastic as managers are often very lenient and are willing to help and communicate with employees.
% Benefits:
% 	Benefits fit with the industry standard, as a full time worker benefits are, employee discount, life insurance, dental, health, glasses, accidental insurance and more.
% Vacation Time:
% 	Vacation time also fit with the industry standard, Vacation hours are accumulated and you could request a vacation three weeks ahead of the date due to the scheduling process. You could have somewhere between two to three weeks of vacation.
% Employee Communications:
% 	As a sales representative, you had great communication with your employer or manager, they are understand and open ended. 
% How well does management perform?
% 	Based on review from former employees, many praised Best Buy for its fantastic management and opprotunities, many have explained it with a great atmosphere, and being very welcoming.
% Training and Skills development
% 	As a sales representative, you are trained to communicate with customers and help them find what they need.
% Community involvement
% 	Best Buy hosts programs which help teach youths a variety of technology. They provide grants to school to give them an opprotunity to get into technology.
	


% Best Buy
% Bank of Canada
% Physical work,
% 	sales representatives are often in the store, working the floor. 


% Work environment,
% 	Based off of reviews online, Best buy seems like a great place to work with good co workers and fair managers

% Benefits
% 	employee discount, life insurance, dental, health, glasses, accidental insurance

% Vacation time
% 	follows industrial standards

% Employee Communications
% 	Seems well based on the workplace culture. 

% How well does management perform?

% Training and Skills development

% Community involvement

\end{document}